Robotic Cart System

### 2020-10-20 systemLevelFunctionalRequirements.tex
Updated the system level presentation
Updated speed requirement

\title{
    \begin{center}
        \href{http://www.bradley.edu}{\includegraphics[height=1in]{figs/logoBU1-Print}}
        \vskip10pt
        \HRule \\[0.4cm]
        {\Huge \bfseries Robotic Cart System \\\Large Project Statement and Functional Requirements}\\[0.4cm] % Degree
        \HRule \\[0.4cm]
    \end{center}
    }
\author{Kallistah Allen, Darrah Beebe, and Jason Braker \\ \underline{Advisor}: Dr. Suruz Miah}

@@

\subsection{System Inputs and Outputs}
\subsubsection{Inputs}
There are four inputs to the robotic cart system.
\begin{enumerate}
    \item Power - Both the mobile cart and the remote will require power from a battery.
    \item On/Off Switch - The user must be able to turn both the cart and the remote off to save power when the robotic cart system is not in use.
    \item Movement of the Remote - The user will control the mobile cart by moving with the remote.
    \item Mode Selection - The user must be able to select which mode of operation the robotic cart system should use.
\end{enumerate}

\subsubsection{Outputs}
There are two outputs from the robotic cart system.
\begin{enumerate}
    \item Cart Position Trajectory on 2D Plane - The cart will move to follow the remote.
    \item Status Indicators - Both the mobile cart and the remote will have status indicators to provide the user with the status of the system.
\end{enumerate}

%------------------------------------------------
\section{Requirements and Specifications}
\subsection{Requirements}
The robotic cart system will meet the following requirements:
\begin{enumerate}
    \item Cart should follow remote at a reasonable distance
    \item Cart should be able to travel at a speed reasonable for walking
    \item User should be alerted if cart falls too far behind
    \item Cart should not require line-of-sight to follow remote
    \item Cart should avoid obstacles
\end{enumerate}

\subsection{Specifications}
Based on the requirements, the robotic cart system must meet the following specifications:
\begin{enumerate}
    \item Cart should be able to follow the remote while maintaining a distance of 1 to 1.5 meters.
    \item Cart should be able to travel at 2 m/s
    \item User should be alerted if the cart falls more than 2 meters behind
    \item Cart should not require line-of-sight to follow remote
    \item Cart should not collide with obstacles while following remote
\end{enumerate}

>>>>

\title{
    \begin{center}
        \href{http://www.bradley.edu}{\includegraphics[height=1in]{figs/logoBU1-Print}}
        \vskip10pt
        \HRule \\[0.4cm]
        {\Huge \bfseries Robotic Cart System \\\Large Project Statement and Functional Requirements}\\[0.4cm] % Degree
        \HRule \\[0.4cm]
    \end{center}
    }
\author{Kallistah Allen, Darrah Beebe, and Jason Braker \\ \underline{Advisors}: Dr. Suruz Miah and Dr. Prasad Shastry}

@@

\subsection{System Inputs and Outputs}
\subsubsection{Inputs}
There are four inputs to the robotic cart system.
\begin{itemize}
    \item Power - Both the mobile cart and the remote will require power from a battery.
    \item On/Off Switch - The user must be able to turn both the cart and the remote off to save power when the robotic cart system is not in use.
    \item Movement of the Remote - The user will control the mobile cart by moving with the remote.
    \item Mode Selection - The user must be able to select which mode of operation the robotic cart system should use.
\end{itemize}

\subsubsection{Outputs}
There are two outputs from the robotic cart system.
\begin{itemize}
    \item Movement of the Cart - The cart will move to follow the remote.
    \item Status Indicators - Both the mobile cart and the remote will have status indicators to provide the user with the status of the system.
\end{itemize}

%------------------------------------------------
\section{Requirements and Specifications}
\subsection{Requirements}
The robotic cart system will meet the following requirements:
\begin{itemize}
    \item Cart should follow remote at a reasonable distance
    \item Cart should be able to travel at a speed reasonable for walking
    \item User should be alerted if cart falls too far behind
    \item Cart should not require line-of-sight to follow remote
    \item Cart should avoid obstacles
\end{itemize}

\subsection{Specifications}
Based on the requirements, the robotic cart system must meet the following specifications:
\begin{itemize}
    \item Cart should be able to follow the remote while maintaining a distance of 1 to 1.5 meters.
    \item Cart should be able to travel at speeds up to 2 m/s
    \item User should be alerted if the cart falls more than 2 meters behind
    \item Cart should not require line-of-sight to follow remote
    \item Cart should not collide with obstacles while following remote
\end{itemize}
